A Global Picture of Food Insecurity and Hunger

### 2020-11-10 docs/modeling_fies.tex
some minor changes in the text of the manuscript

Examining the rate of food insecurity in a population, rather than the total number of food insecure people (See Fig. \ref{fig:rates}, our model finds the most progress has been made in East \& Southeast Asia, while Central \& Southern Asia is expected to see improvements in food insecurity throughout the 2020s.  Other poor and middle income areas, including much of Africa, the Middle East and Latin America, have made only slight progress and will continue to make slight progress between 2010 and 2030.  In high-income countries in Europe and North America, rates of people in at least moderate food insecurity move little, and rates of severe food insecurity are expected to increase slightly.  Overall, the world has made has made steady but slow progress on reducing the rate of food insecurity.

@@

\subsection{Food Insecurity over Space}
We found substantial heterogeneity in the global distribution of severe food insecurity (See Fig. \ref{fig:map}).  For the year 2020, mainland sub-Saharan Africa is the continent with with the highest rates of severe food insecurity, with at least 15\% of people over the threshold for severe food insecurity in at last one subnational area in every country except Gabon and Equatorial Guinea.  Outside of Africa, serious pockets of severe food insecurity also occur in Venezuela, Syria, Papua New Guinea, Yemen, and Afghanistan.  In many large middle-income countries, severe food insecurity is also quite prevalent, with rates between 10-15\% in areas like northern Brazil, many central Asian and middle-eastern countries, and India and Indonesia.

@@

Additionally, when making predictions into the future, we are assuming that long-term patterns of demographic change, urbanization, and development will maintain their long-held trajectories for the next decade.  At a global scale, this is almost certainly the case: it is highly unlikely that rates of fertility or economic growth with shift suddenly and globally.  Nevertheless, at more local scales, sudden crises can lead to severe and unforeseeable increases in food insecurity, as crises in the previous decade in Yemen, Syria and Venezuela have shown.  Thus, while our model's predictions at a global scale are very likely to bear out, there will probably be individual countries and areas where our forecasts end up being off.

>>>>

Examining the rate of food insecurity in a population, rather than the total number of food insecure people (See Fig. \ref{fig:rates}, our model finds the most progress has been made in East \& Southeast Asia, while Central \& Southern Asia is expected to see improvements in food insecurity throughout the 2020s.  Other poor and middle income areas, including much of Africa, the Middle East and Latin America, have made only slight progress and will continue to make slight progress between 2010 and 2030.  In high-income countries in Europe and North America, rates of people in at least moderate food insecurity move little, and rates of severe food insecurity are expected to increase slightly.  Overall, the world has made steady but slow progress on reducing the rate of food insecurity.

@@

\subsection{Food Insecurity over Space}
We found substantial heterogeneity in the global distribution of severe food insecurity (See Fig. \ref{fig:map}).  For the year 2020, mainland sub-Saharan Africa is the continent with the highest rates of severe food insecurity, with at least 15\% of people over the threshold for severe food insecurity in at last one subnational area in every country except Gabon and Equatorial Guinea.  Outside of Africa, serious pockets of severe food insecurity also occur in Venezuela, Syria, Papua New Guinea, Yemen, and Afghanistan.  In many large middle-income countries, severe food insecurity is also quite prevalent, with rates between 10-15\% in areas like northern Brazil, many central Asian and middle-eastern countries, and India and Indonesia.

@@

Additionally, when making predictions into the future, we are assuming that long-term patterns of demographic change, urbanization, and development will maintain their long-held trajectories for the next decade.  At a global scale, this is almost certainly the case: it is highly unlikely that rates of fertility or economic growth will shift suddenly and globally.  Nevertheless, at more local scales, sudden crises can lead to severe and unforeseeable increases in food insecurity, as crises in the previous decade in Yemen, Syria and Venezuela have shown.  Thus, while our model's predictions at a global scale are very likely to bear out, there will probably be individual countries and areas where our forecasts end up being off.
